---
title: "Epidome sequence analysis"
output:
  html_notebook:
    toc: yes
author: "Thor Bech Johannesen, Statens Serum Institut"
---

## **Classification of dada2 generated ASVs, creation of barplots, PCA plots and more**

### Load functions

```{r}
source("https://raw.githubusercontent.com/ssi-dk/epidome/master/scripts/epidome_functions.R")
```

### Read in data. Required data is:
### Table containing frequencies of STs and amplicons (found in github repo)
### Sequence count tables in dada2 format created by running ASV_blast_classification.py on dada2 ASV table output
### OPTIONAL: metadata table. Row names must match column names in dada output.
```{r}
ST_amplicon_table = read.table("DB/epidome_ST_amplicon_frequencies.txt",sep = "\t")

epi01_table = read.table("example_data/190920_run2_g216_test.csv",sep = ";",header=TRUE,row.names=1)
epi02_table = read.table("example_data/190920_run2_yycH_test.csv",sep = ";",header=TRUE,row.names=1)
metadata_table = read.table("example_data/article_metadata.txt",header=TRUE,row.names=1)
```


### Setup object for data handling
```{r}
epidome_object = setup_epidome_object(epi01_table,epi02_table,metadata_table = metadata_table)
```

### Check how well the output from the two primer sets align. Color_variable can be left out
```{r}
compare_primer_output(epidome_object,color_variable = "sample.type")
```

### Combine ASVs assigned to the same taxa
```{r}
eo_ASV_combined = combine_ASVs_epidome(epidome_object)
```



### Remove low count samples from data set. (Only include samples where number of sequences from primer1 >= x and sequences form primer2 >= y)
```{r}
eo_filtered = filter_lowcount_samples_epidome(eo_ASV_combined,500,500)
```

### Assign ASVs to STs on a per sample basis and make barplot
```{r}
count_table = classify_epidome(eo_filtered,ST_amplicon_table)
p = make_barplot_epidome(count_table,reorder=TRUE,normalize=TRUE)
p
```





